Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-11-22 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
went through Section 4

We thus propose a constrained clustering algorithm that preserves sequences of operations by considering their order in the assignment to clusters. That is, the predecessors of an operation to be put into the $n$th cluster must be assigned to clusters $1,\dots,n$. 
%More specifically, it is not allowed to insert a data object (\textit{an operation}) in a particular cluster, and the predecessor of that operation is not assigned yet to the same cluster or the preceding cluster(s). 
Considering that our approach involves cluster-wise combinatorial optimization, the generation of large clusters might deteriorate the solving performance significantly.
In the extreme case, all operations could be put into a single cluster representing the entire problem instance.
% finding a solution for a sub-problem might require the same time as the solution of the whole problem.
Hence, in addition to the similarity of operations, our decomposition method also aims at balancing the number of operations per cluster.

@@

%            \If{$pred\_selected\_data\_obj \notin clus$}     \Comment{Satisfying the precedence constraint}
%                \State $curr\_clus \gets pred\_selected\_data\_obj$
%            \EndIf
            \State Update the $n$th centroid % $update\_centroid$
%            \State $count\_cap \gets count\_cap + 1 $
    \EndWhile
%      \State $count\_clus \gets count\_clus + 1 $
%  \EndWhile
  \EndFor
%  \State \Return $\mathit{clusters}$
  \end{algorithmic}
  \end{algorithm}
%
Algorithm~\ref{alg2} provides a pseudocode description of our constrained clustering algorithm.
Similar to K-Means, we assume that the algorithm gets the target number of clusters 
into which the operations shall be partitioned as input.
The cluster capacity, used for balancing the operations per cluster, is then obtained by dividing the total number of operations by the number of clusters.
Moreover, the clustering process takes care of generating one initial centroid per cluster, given by randomly selected operations that are compatible with the precedence relation.
For example, when each job consists of $15$ operations and the target number of clusters is $3$,
the first centroid will be an operation at the first to fifth place of its job,
the second an operation from place six to ten, and the third an operation at the eleventh
or later place.
% After generating the centroids, we check for exceeding the number of clusters and the cluster capacity, respectively. 
%
Next, the algorithm calculates the distance between each operation and the centroid of the current cluster using Euclidean distance and assigns the nearest operation to that cluster. In order to satisfy the precedence constraint, we check the assignments of predecessors. If the constraint is satisfied, the algorithm assigns the operation to the cluster, and the centroid is updated. Whenever the maximum number of operations is reached, the algorithm continues with the next cluster. These iterations continue until all operations are assigned to some cluster. 
%
\iffalse
\begin{figure}[h!]
  \includegraphics[width=\linewidth]{Flow_chart_9.png}
  \caption{Flowchart of the proposed Clustering Algorithm.}
  \label{fig1}
\end{figure}
\fi

Our main procedure starts with the selection of a subset of the extracted features, which allows the clustering algorithm to compute the best possible time window assignments. 
The procedure follows the forward feature selection principle: start with a small set of features and in every iteration extends it with one feature.
Run the clustering algorithm on the new set of features and solve the obtained sequence of time windows. The subset of features resulting in the best possible solution quality is preserved and provided for extension in the next loop of the feature selection algorithm. The latter continues until either 
\begin{enumerate*}[label=\emph{(\roman*)}]
  \item all features are included in the target set, or 
  \item any extension of the provided subset of features results in solutions of worse quality than the solution of the given set.
\end{enumerate*}

>>>>

We thus propose a constrained clustering algorithm that preserves sequences of operations by considering their order in the assignment to clusters. That is, the predecessors of an operation to be put into the $n$th cluster must be assigned within the clusters $1,\dots,n$. 
%More specifically, it is not allowed to insert a data object (\textit{an operation}) in a particular cluster, and the predecessor of that operation is not assigned yet to the same cluster or the preceding cluster(s). 
Also considering that our approach involves cluster-wise combinatorial optimization, the generation of large clusters risks to deteriorate the solving performance significantly.
In the extreme case, all operations could be put into a single cluster representing the entire problem instance.
% finding a solution for a sub-problem might require the same time as the solution of the whole problem.
Hence, in addition to the similarity of operations, our decomposition method also aims at balancing the number of operations per cluster.

@@

%            \If{$pred\_selected\_data\_obj \notin clus$}     \Comment{Satisfying the precedence constraint}
%                \State $curr\_clus \gets pred\_selected\_data\_obj$
%            \EndIf
            \State Update the $n$th centroid % $update\_centroid$
%            \State $count\_cap \gets count\_cap + 1 $
    \EndWhile
%      \State $count\_clus \gets count\_clus + 1 $
%  \EndWhile
  \EndFor
%  \State \Return $\mathit{clusters}$
  \end{algorithmic}
  \end{algorithm}
%
Algorithm~\ref{alg2} provides a pseudocode description of our constrained clustering algorithm.
Similar to K-Means, we assume that the algorithm gets the target number of clusters 
into which the operations shall be partitioned as input.
The cluster capacity, used for balancing the operations per cluster, is then obtained by dividing the total number of operations by the number of clusters.
Moreover, the clustering algorithm takes care of generating one initial centroid per cluster, given by randomly selected operations that are compatible with the precedence relation.
For example, when each job consists of $15$ operations and the target number of clusters is $3$,
the first centroid will be an operation at the first to fifth place of its job,
the second an operation from place six to ten, and the third an operation at the eleventh
or later place.
% After generating the centroids, we check for exceeding the number of clusters and the cluster capacity, respectively. 
%
In order to populate each cluster, the algorithm inspects features to determine the Euclidean distance of each yet unassigned operation to the centroid of the current cluster and assigns the nearest operation to the cluster. To also preserve the precedence between operations, we additionally include any yet unassigned predecessor operations in the current cluster, and then update its centroid with the features of newly assigned operations. Whenever the cluster capacity is reached, the algorithm proceeds to the next cluster, and this decomposition process continues until all operations are assigned to clusters.
%
\iffalse
\begin{figure}[h!]
  \includegraphics[width=\linewidth]{Flow_chart_9.png}
  \caption{Flowchart of the proposed Clustering Algorithm.}
  \label{fig1}
\end{figure}
\fi

In order to identify the most promising features for distance calculation among those introduced in the previous section,
we applied the following forward selection principle:
% Our main procedure starts with the selection of a subset of the extracted features, which allows the clustering algorithm to compute the best possible time window assignments. 
% The procedure follows the forward feature selection principle:
start with a small set of features, perform decomposition by Algorithm~\ref{alg2},
and iteratively solve JSP instances.
Then, we evaluate the possible extensions by one more feature,
compare the quality of resulting schedules, and pick the best set of features. 
% and in every iteration extends it with one feature.
% Run the clustering algorithm on the new set of features and solve the obtained sequence of time windows. The subset of features resulting in the best possible solution quality is preserved and provided for extension in the next loop of the feature selection algorithm.
This process continues until either 
\begin{enumerate*}[label=\emph{(\roman*)}]
  \item all features are selected, or 
  \item any extension by another feature leads to solutions of lower quality.
\end{enumerate*}
